---
title: "FIFA 2017 player Analysis"
author: "Hitesh Vedwal"
date: "10 November 2017"
output: html_document
---


In this script we'd be look at following Analytics.
* [1.Which continent player’s are best at particular Attribute.](#Whichcontinentplayer'sarebest)
* [2.On Field Behaviour of the Players.](#OnFieldBehaviour)
* [3.Analytics on contract period.](#COntract period)
* [4.Age Density of FIFA Players](#AgeDensity)
* [5.RadarChart for top 10 players.](#RadarChart)

* [Import data](#Importdata)


```{r, message=FALSE, warning=FALSE}
# Importing Library
library(readr)
library(data.table)
library(sqldf)
library(radarchart)
library(tidyr)
library("knitr")
library(DT)
library(ggplot2)
```

##Import data{#Importdata}

```{r, message=FALSE, warning=FALSE}
FullData <- read_csv("C:/Users/vdwal/Desktop/mini project 5th sem/FIFA Dataset/FullData.csv")
setDT(FullData)
names(FullData)
dim(FullData)
kable(head(FullData)) 

# Unique values per column
#lapply(FullData, function(x) length(unique(x))) 

```

##Which continent player's are best at which particular Attribute.

####Approach(Player Attribute- Ball_Control, Dribbling, Marking, Attacking_Position, Acceleration, Speed, Stamina, Strength, Balance, Crossing).
####1.Selecting players with each attribute.
####2.Then group by Nationality.
####3.Sum players each attribute by nationality group, list in descending order.
```{r}
library(dplyr)
Data1_df<- FullData

Ball_controldf <- arrange(Data1_df, desc(Ball_Control))
Ball_controldf <- filter(Ball_controldf, Ball_Control >= 90)
Ball_Control_list <- Ball_controldf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Ball_Control_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Dribbling_df <- arrange(Data1_df, desc(Dribbling))
Dribbling_df <- filter(Dribbling_df, Dribbling >= 90)
Dribbling_list <- Dribbling_df %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Dribbling_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Markingdf <- arrange(Data1_df, desc(Marking))
Markingdf <- filter(Markingdf, Marking >= 90)
Marking_list <- Markingdf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Marking_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Attacking_Positiondf <- arrange(Data1_df, desc(Attacking_Position))
Attacking_Positiondf <- filter(Attacking_Positiondf, Attacking_Position >= 90)
Attacking_Position_list <- Attacking_Positiondf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Attacking_Position_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Accelerationdf <- arrange(Data1_df, desc(Acceleration))
Accelerationdf <- filter(Accelerationdf, Acceleration >= 90)
Acceleration_list <- Accelerationdf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Acceleration_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Speeddf <- arrange(Data1_df, desc(Speed))
Speeddf <- filter(Speeddf, Speed >= 90)
Speed_list <- Speeddf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Speed_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Staminadf <- arrange(Data1_df, desc(Stamina))
Staminadf <- filter(Staminadf, Stamina >= 90)
Stamina_list <- Staminadf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Stamina_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Strengthdf <- arrange(Data1_df, desc(Strength))
Strengthdf <- filter(Strengthdf, Strength >= 90)
Strength_list <- Strengthdf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Strength_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Balancedf <- arrange(Data1_df, desc(Balance))
Balancedf <- filter(Balancedf, Balance >= 90)
Balance_list <- Balancedf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Balance_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))

Crossingdf <- arrange(Data1_df, desc(Crossing))
Crossingdf <- filter(Crossingdf, Crossing >= 90)
Crossing_list <- Crossingdf %>% group_by(Nationality)  %>% summarise(n = n()) %>% arrange(desc(n))
datatable(Crossing_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))
```

**2.Looking at Continent level, Made a list of Continent_contries.**

```{r, message=FALSE, warning=FALSE}
africa<-c('Algeria','Angola','Benin','Botswana','Burkina','Burundi','Cameroon','Cape Verde','Central African Republic','Chad','Comoros','Congo','Congo Democratic Republic of','Djibouti','Egypt','Equatorial Guinea','Eritrea','Ethiopia','Gabon','Gambia','Ghana','Guinea','Guinea-Bissau','Ivory Coast','Kenya','Lesotho','Liberia','Libya','Madagascar','Malawi','Mali','Mauritania','Mauritius','Morocco','Mozambique','Namibia','Niger','Nigeria','Rwanda','Sao Tome and Principe','Senegal','Seychelles','Sierra Leone','Somalia','South Africa','South Sudan','Sudan','Swaziland','Tanzania','Togo','Tunisia','Uganda','Zambia','Zimbabwe','Burkina Faso')
asia<-c('Afghanistan','Bahrain','Bangladesh','Bhutan','Brunei','Burma (Myanmar)','Cambodia','China','East Timor','India','Indonesia','Iran','Iraq','Israel','Japan','Jordan','Kazakhstan','North Korea','South Korea','Kuwait','Kyrgyzstan','Laos','Lebanon','Malaysia','Maldives','Mongolia','Nepal','Oman','Pakistan','Philippines','Qatar','Russian Federation','Saudi Arabia','Singapore','Sri Lanka','Syria','Tajikistan','Thailand','Turkey','Turkmenistan','United Arab Emirates','Uzbekistan','Vietnam','Yemen','Russia')
europe<-c('Albania','Andorra','Armenia','Austria','Azerbaijan','Belarus','Belgium','Bosnia Herzegovina','Bulgaria','Croatia','Cyprus','Czech Republic','Denmark','Estonia','Finland','France','Georgia','Germany','Greece','Hungary','Iceland','Ireland','Italy','Latvia','Liechtenstein','Lithuania','Luxembourg','Macedonia','Malta','Moldova','Monaco','Montenegro','Netherlands','Norway','Poland','Portugal','Romania','San Marino','Serbia','Slovakia','Slovenia','Spain','Sweden','Switzerland','Ukraine','England','Vatican City','Republic of Ireland','Wales')
north_america<-c('Antigua and Barbuda','Bahamas','Barbados','Belize','Canada','Costa Rica','Cuba','Dominica','Dominican Republic','El Salvador','Grenada','Guatemala','Haiti','Honduras','Jamaica','Mexico','Nicaragua','Panama','Saint Kitts and Nevis','Saint Lucia','Saint Vincent and the Grenadines','Trinidad and Tobago','United States')
oceania<-c('Australia','Fiji','Kiribati','Marshall Islands','Micronesia','Nauru','New Zealand','Palau','Papua New Guinea','Samoa','Solomon Islands','Tonga','Tuvalu','Vanuatu')
south_america<-c('Argentina','Bolivia','Brazil','Chile','Colombia','Ecuador','Guyana','Paraguay','Peru','Suriname','Uruguay','Venezuela')
others<-c('DR Congo', 'Korea Republic', 'Northern Ireland', 'Scotland', 'Guinea Bissau', 'Kosovo', 'São Tomé & Príncipe', 'Curacao', 'FYR Macedonia', 'FIFA16_NationName_215', 'Palestine', 'Bermuda', 'Central African Rep.', 'St Kitts Nevis', 'Trinidad & Tobago', 'China PR', 'Aruba', 'Guam', 'Chinese Taipei', 'Faroe Islands', 'Montserrat', 'Puerto Rico', 'Antigua & Barbuda', 'Korea DPR', 'Gibraltar', 'Timor-Leste', 'St Lucia')
```

**chainging country by continent name**

```{r, message=FALSE, warning=FALSE}
library(dplyr)
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% africa] <- "africa"
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% asia] <- "asia"
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% europe] <- "europe"
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% north_america] <- "north_america"
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% oceania]<-"oceania"
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% south_america]<-"south_america"
Ball_Control_list$Nationality[Ball_Control_list$Nationality %in% others]<-"others"

unique(Ball_Control_list$Nationality) # Check for nationality values

Ball_Control_list <- Ball_Control_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Ball_Control_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Dribbling_list$Nationality[Dribbling_list$Nationality %in% africa] <- "africa"
Dribbling_list$Nationality[Dribbling_list$Nationality %in% asia] <- "asia"
Dribbling_list$Nationality[Dribbling_list$Nationality %in% europe] <- "europe"
Dribbling_list$Nationality[Dribbling_list$Nationality %in% north_america] <- "north_america"
Dribbling_list$Nationality[Dribbling_list$Nationality %in% oceania]<-"oceania"
Dribbling_list$Nationality[Dribbling_list$Nationality %in% south_america]<-"south_america"
Dribbling_list$Nationality[Dribbling_list$Nationality %in% others]<-"others"

unique(Dribbling_list$Nationality) # Check for nationality values

Dribbling_list <- Dribbling_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Dribbling_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))



Marking_list$Nationality[Marking_list$Nationality %in% africa] <- "africa"
Marking_list$Nationality[Marking_list$Nationality %in% asia] <- "asia"
Marking_list$Nationality[Marking_list$Nationality %in% europe] <- "europe"
Marking_list$Nationality[Marking_list$Nationality %in% north_america] <- "north_america"
Marking_list$Nationality[Marking_list$Nationality %in% oceania]<-"oceania"
Marking_list$Nationality[Marking_list$Nationality %in% south_america]<-"south_america"
Marking_list$Nationality[Marking_list$Nationality %in% others]<-"others"

unique(Marking_list$Nationality) # Check for nationality values

Marking_list <- Marking_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Marking_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))



Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% africa] <- "africa"
Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% asia] <- "asia"
Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% europe] <- "europe"
Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% north_america] <- "north_america"
Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% oceania]<-"oceania"
Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% south_america]<-"south_america"
Attacking_Position_list$Nationality[Attacking_Position_list$Nationality %in% others]<-"others"

unique(Attacking_Position_list$Nationality) # Check for nationality values

Attacking_Position_list <- Attacking_Position_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Attacking_Position_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Acceleration_list$Nationality[Acceleration_list$Nationality %in% africa] <- "africa"
Acceleration_list$Nationality[Acceleration_list$Nationality %in% asia] <- "asia"
Acceleration_list$Nationality[Acceleration_list$Nationality %in% europe] <- "europe"
Acceleration_list$Nationality[Acceleration_list$Nationality %in% north_america] <- "north_america"
Acceleration_list$Nationality[Acceleration_list$Nationality %in% oceania]<-"oceania"
Acceleration_list$Nationality[Acceleration_list$Nationality %in% south_america]<-"south_america"
Acceleration_list$Nationality[Acceleration_list$Nationality %in% others]<-"others"

unique(Acceleration_list$Nationality) # Check for nationality values

Acceleration_list <- Acceleration_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Acceleration_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))



Speed_list$Nationality[Speed_list$Nationality %in% africa] <- "africa"
Speed_list$Nationality[Speed_list$Nationality %in% asia] <- "asia"
Speed_list$Nationality[Speed_list$Nationality %in% europe] <- "europe"
Speed_list$Nationality[Speed_list$Nationality %in% north_america] <- "north_america"
Speed_list$Nationality[Speed_list$Nationality %in% oceania]<-"oceania"
Speed_list$Nationality[Speed_list$Nationality %in% south_america]<-"south_america"
Speed_list$Nationality[Speed_list$Nationality %in% others]<-"others"

unique(Speed_list$Nationality) # Check for nationality values

Speed_list <- Speed_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Speed_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Stamina_list$Nationality[Stamina_list$Nationality %in% africa] <- "africa"
Stamina_list$Nationality[Stamina_list$Nationality %in% asia] <- "asia"
Stamina_list$Nationality[Stamina_list$Nationality %in% europe] <- "europe"
Stamina_list$Nationality[Stamina_list$Nationality %in% north_america] <- "north_america"
Stamina_list$Nationality[Stamina_list$Nationality %in% oceania]<-"oceania"
Stamina_list$Nationality[Stamina_list$Nationality %in% south_america]<-"south_america"
Stamina_list$Nationality[Stamina_list$Nationality %in% others]<-"others"

unique(Stamina_list$Nationality) # Check for nationality values

Stamina_list <- Stamina_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Stamina_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Strength_list$Nationality[Strength_list$Nationality %in% africa] <- "africa"
Strength_list$Nationality[Strength_list$Nationality %in% asia] <- "asia"
Strength_list$Nationality[Strength_list$Nationality %in% europe] <- "europe"
Strength_list$Nationality[Strength_list$Nationality %in% north_america] <- "north_america"
Strength_list$Nationality[Strength_list$Nationality %in% oceania]<-"oceania"
Strength_list$Nationality[Strength_list$Nationality %in% south_america]<-"south_america"
Strength_list$Nationality[Strength_list$Nationality %in% others]<-"others"

unique(Strength_list$Nationality) # Check for nationality values

Strength_list <- Strength_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Strength_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))



Balance_list$Nationality[Balance_list$Nationality %in% africa] <- "africa"
Balance_list$Nationality[Balance_list$Nationality %in% asia] <- "asia"
Balance_list$Nationality[Balance_list$Nationality %in% europe] <- "europe"
Balance_list$Nationality[Balance_list$Nationality %in% north_america] <- "north_america"
Balance_list$Nationality[Balance_list$Nationality %in% oceania]<-"oceania"
Balance_list$Nationality[Balance_list$Nationality %in% south_america]<-"south_america"
Balance_list$Nationality[Balance_list$Nationality %in% others]<-"others"

unique(Balance_list$Nationality) # Check for nationality values

Balance_list <- Balance_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Balance_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))


Crossing_list$Nationality[Crossing_list$Nationality %in% africa] <- "africa"
Crossing_list$Nationality[Crossing_list$Nationality %in% asia] <- "asia"
Crossing_list$Nationality[Crossing_list$Nationality %in% europe] <- "europe"
Crossing_list$Nationality[Crossing_list$Nationality %in% north_america] <- "north_america"
Crossing_list$Nationality[Crossing_list$Nationality %in% oceania]<-"oceania"
Crossing_list$Nationality[Crossing_list$Nationality %in% south_america]<-"south_america"
Crossing_list$Nationality[Crossing_list$Nationality %in% others]<-"others"

unique(Crossing_list$Nationality) # Check for nationality values

Crossing_list <- Crossing_list %>% group_by(Nationality) %>% summarise(n = n()) %>% arrange(desc(n)) 
datatable(Crossing_list, style="bootstrap", class="table-condensed", options = list(dom = 'tp',scrollX = TRUE))
```
```{r, message=FALSE, warning=FALSE, echo=FALSE }
ggplot(Speed_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Speed Group By Nationality') +
  theme_bw()

ggplot(Crossing_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Crossing Group By Nationality') +
  theme_bw()


ggplot(Balance_list, aes(x = n, y =  reorder(Nationality, n) )) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Balance Group By Nationality') +
  theme_bw()

ggplot(Strength_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Strength Group By Nationality') +
  theme_bw()

ggplot(Stamina_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Stamina Group By Nationality') +
  theme_bw()

ggplot(Acceleration_list, aes(x = n, y = reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Acceleration Group By Nationality') +
  theme_bw()

ggplot(Attacking_Position_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Attaacking Position Group By Nationality') +
  theme_bw()

ggplot(Marking_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Marking Group By Nationality') +
  theme_bw()

ggplot(Dribbling_list, aes(x = n, y = reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Dribbling Group By Nationality') + 
  theme_bw()

ggplot(Ball_Control_list, aes(x = n, y =  reorder(Nationality, n))) +
  geom_bar(stat='identity',colour="white", fill = c("magenta")) +
  labs(x = 'Count', y = 'Nationality', title = 'Ball Control Group By Nationality') +
  theme_bw()
```

##On Field Behaviour of Top 1000 Players.
####Approach(Player Attribute- Aggression, Reactions, Attacking_Position, Interceptions, Vision, Composure, Agility).
####Subsetting the required attribute in a Data Frame.
```{r, message=FALSE, warning=FALSE, echo=FALSE}
Data <- subset(FullData, select = c("Aggression", "Reactions", "Attacking_Position", "Interceptions", "Vision", "Composure", "Agility"))
Data_df <- tbl_df(Data)
behave_df <- head(arrange(Data_df, Aggression, Reactions, Attacking_Position, Interceptions, Vision, Composure, Agility), n = 1000)

```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
require(reshape2)
a <- melt(behave_df, id.vars = "Agility")

ggplot(data = a, aes(x=variable, y=value)) + 
  geom_jitter(aes(colour=variable))
```

#Analytics on contract period
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(lubridate)
library(plyr)
# Creating the dataframe containing the required attribute
Contract_period_df<- tbl_df(subset(FullData, select = c("Name","Club_Joining", "Contract_Expiry")))
#Data frame having the contract Period from There Joining Date to Contract Expiry
a = mdy(Contract_period_df$Club_Joining)
club_joining_year <- year(a)
CP <- Contract_period_df$Contract_Expiry - club_joining_year

Contract_period <- CP

data <- tbl_df(cbind(Contract_period_df, club_joining_year, Contract_period))
# Grouping the Number of Players with Contract Period
unique <- tbl_df(unique(data$Contract_period))
frequency <- count(data, 'Contract_period')
```
```{r, message=FALSE, warning=FALSE, echo=FALSE}
ggplot(frequency, aes(Contract_period,freq))+
  geom_point(aes(colour = Contract_period))+
  labs(x = 'Contract Period', y = 'No. of Players')
```
## Age Density of FIFA Players {#AgeDensity}

```{r, message=FALSE, warning=FALSE}

ggplot(FullData, aes(Age, fill = Age)) +
geom_density(position = "stack")

```
## Radar Chart for Top 50 players
```{r, message=FALSE, warning=FALSE}
library(radarchart)
library(tidyr)
#Selecting top players by rating from data
top50 <- head(FullData, 50)

radarDF <- top50 %>% select(Name, 20:53) %>% as.data.frame()

radarDF <- gather(radarDF, key=Label, value=Score, -Name) %>%
  spread(key=Name, value=Score)

chartJSRadar(scores = radarDF, maxScale = 100, showToolTipLabel = TRUE)
```
